\documentclass[a4paper,11pt]{article}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage[T1]{fontenc} % if needed

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% My Packages %%%%%%%%%%%%%%%%%
\usepackage[english]{babel}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{physics,slashed}
\usepackage{graphicx}
\usepackage[toc,page]{appendix}
\usepackage{hyperref}
\usepackage[noabbrev]{cleveref}

\usepackage{xcolor}
\usepackage{mdframed}

\usepackage[hmarginratio=1:1]{geometry}

\begin{document}

We appreciate the referee's careful review of our manuscript and the insightful feedback
provided. Below, we provide detailed responses to each point and explain the
corresponding changes made to the manuscript where applicable:

\begin{enumerate}
      \item
            \begin{enumerate}
                  \item  To obtain the matter Lagrangian for this model, we use the Schutz
                        formalism, following Ref.~\cite{fluidgeral}. In this framework, the
                        Lagrangian corresponds to the fluid pressure, which depends on the
                        specific entropy and enthalpy. A detailed discussion of this
                        approach is provided in the cited reference. For clarity, we rewrote
                        the description of the Schutz formalism in Section 2.2 and ensured
                        that the references are correctly cited.

                  \item Indeed, if the sound speed were to approach zero, we would encounter
                        a divergence problem. This is why we limit ourselves to small but
                        non-zero equations of state for dust, which is in agreement with the
                        literature. Regarding the $\zeta$ field, there are always field
                        configurations that would lead to non-perturbative behavior.
                        However, in the present context, given the initial conditions in
                        equation 3.32, we are considering the adiabatic vacuum for which
                        $\zeta \propto 1/\sqrt{z^2c_s} \propto \sqrt{c_s}$. Therefore, terms
                        of the form $z^2c_s^2\zeta^2$ are $\propto c_s$ while $\zeta^3
                              \propto \sqrt{c_s}^3$ This means that the perturbative expansion is valid
                        for small sound speeds, as discussed in
                        Ref.~\cite{vitenti2012large}.

                        We have reorganized Sections 4.3 and 4.4 and considered a very
                        small, but non-zero, equation of state for dark matter to analyze
                        the pressureless case.
            \end{enumerate}

      \item

            \begin{enumerate}
                  \item We improved Sec.~2.2 by adding a more detailed explanation of the
                        Schutz formalism and the fluid Lagrangian. We also included a
                        discussion of the lapse function and how it can be defined as a
                        posteriori for simplicity.

                  \item In the improved Sec.~2.2, we have added a brief discussion of the
                        meaning of the effective energy density and pressure in the context
                        of the quantum corrections. In Ref.~\cite{fluidgeral}, the authors
                        show that the energy density and pressure appearing in the perturbed
                        equations are only the classical ones computed with the Bohmian
                        trajectory. Therefore, the equation-of-state parameter is always
                        $w=p_d/\rho_d$.

                  \item In the revised Sec.~2.2, we have included the effective equation
                        corresponding to the second Friedmann equation, now presented as Eq. 2.17:
                        $-2\dot{\bar{H}} = \bar{\rho}(1+w) - 2\rho_q.$
                        Notably, the right-hand side of this equation approaches zero around the
                        bounce. However, as discussed previously in Ref.~\cite{fluidgeral} it
                        has been shown that the energy density and pressure in the second-order
                        Lagrangian for the perturbations are only the classical components
                        evaluated along the Bohmian trajectory. Consequently, this term is never
                        zero, ensuring that the model is free from ghost instability issues.
                  \item In Ref.~33 the author chooses a particular form for the wave
                        function at the bounce. This is indeed not an initial condition, but
                        a choice made to simplify the analysis. The same wave-function
                        propagated to $T\to-\infty$ would have an extra phase factor
                        proportional to the $q^2$, exactly like a wave function of a
                        free Gaussian package in 1d. One can always start with a different
                        wave function and define the bounce as the time where the phase
                        factor proportional to $q^2$ is zero. Again, this is equivalent to a
                        free Gaussian package in 1d. Thus, in short, it has to start at a large
                        but finite negative time, with a Gaussian wave-function containing a
                        phase factor proportional to $q^2$. Then, the bounce is defined as
                        the time when this phase factor is zero. We have included a brief
                        discussion of this point in the revised manuscript.
                  \item In our approach, we use a perturbative method: the background is
                        solved first, and the Bohmian trajectory is derived from the
                        background wave function. Perturbations are then computed
                        conditioned on this Bohmian trajectory. In practice, during the
                        contraction phase, the significant part of the power spectrum is
                        generated in the classical regime, effectively following a
                        semi-classical approach. Quantum effects on the background become
                        relevant only near the bounce, where the relevant modes are on
                        super-Hubble scales. If the background is in a superposition of
                        Gaussian states, the perturbations would naturally reflect this
                        superposition. However, this aspect lies outside the scope of our
                        work, as we are focused here on black hole formation during the
                        contraction phase.

            \end{enumerate}

      \item In general, when both the background and the perturbations are quantized it is necessary
            to develop the second order Lagrangian for the perturbations without assuming the background
            is classical. Once this is done, one can show that for particular choices of the wave function
            for the whole system (background plus perturbations), the perturbations can be treated as
            quantum fields evolving around the Bohmian trajectory. We included a brief discussion of this
            point in the revised manuscript, Sec.~3.3.

      \item In Ref.~\cite{vitenti2012large}, it is shown that for a Friedmann background with
            scalar perturbations, an appropriate gauge choice ensures the perturbative
            series remains valid in the bounce model. Nevertheless, this only shows that
            vacuum initial conditions around an initial Friedmann background are
            consistent with the perturbative expansion. The referee is correct in pointing
            out that the perturbative expansion may not be valid for more general initial
            conditions. In our study, we focus on this simpler model, leaving the
            exploration of a homogeneous and anisotropic background, specifically
            Bianchi-I models, for future work. A brief discussion of this possibility has
            been included in the conclusion.

      \item To simplify the presentation, we set the speed of light $c=1$ in the main
            text. We have now included a brief discussion of this choice in the revised
            manuscript. We also clarified the definition of energy density and perturbation
            in the main text.
\end{enumerate}

We hope that these changes address the referee's concerns and improve the clarity of
the manuscript.

\bibliographystyle{unsrt}
\bibliography{g}
\end{document}
